---
title: "Excel to R Equivalents"
author: "R for the Rest of Us"
output: 
    html_document:
        css: style.css
        toc: true
        toc_depth: 1
        toc_float: true
        df_print: paged
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)
```

```{r echo = FALSE}
library(tidyverse)
```

# Introduction

This is a demonstration of Excel to R equivalents. Specifically, I am showing equivalents of six key functions from the [`dplyr` package](http://dplyr.tidyverse.org).

Data comes from the [US National Health and Nutrition Examination Survey](https://www.cdc.gov/nchs/nhanes/index.htm) and was collected from the [NHANES package](https://cran.r-project.org/web/packages/NHANES/index.html). It is a sample of 10,000 people, weighted to be representative of the US population. 

I used the [`clean_names`](https://sfirke.github.io/janitor/reference/clean_names.html) function from the janitor package to make the variable names easy to work with.


# Get Data

Let's import the NHANES data into a data frame and then take a look at it.

```{r}
nhanes <- read_csv("nhanes.csv") 

nhanes
```


# Get Data

I've also made a codebook in case you want to learn more about the variables (most are self-explanatory from their names).

```{r}
nhanes_codebook <- read_csv("nhanes-codebook.csv") 

nhanes_codebook
```


# select


```{r}
nhanes %>% 
  select(height)
```

# mutate


```{r}
nhanes %>%
  mutate(height_inches = height / 2.54) %>% 
  select(height, height_inches)
```


# filter

```{r}
nhanes %>% 
  filter(height > 150) %>% 
  select(height)
```

# summarize

```{r}
nhanes %>% 
  summarize(mean_height = mean(height, na.rm = TRUE))
```


# group_by 

```{r}
nhanes %>% 
  group_by(gender) %>% 
  summarize(mean_height = mean(height, na.rm = TRUE))
```


# arrange 

```{r}
nhanes %>% 
  arrange(height) %>% 
  select(height)
```

